Energy and the CES production function

### 2015-08-22 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Move new sigma graph lower. 2nd option.

Clean up labeling, etc. later.

@@

<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
### A function named blah_function should return a function, not a plot.  Don't use function in the name 
### of a function unless it tells you something about the function.  All functions are functions, we don't
### need to name them like that.

sigma_graph <- function(data){
  sigma_graph_data <- 
    data %>% 
    select(Country, CSP, flavor, energy, nest, 
           sigma_12, sigma_23, sigma_13, 
           sigma_12_3, sigma_23_1, sigma_13_2) %>%
    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
      nest, 
      from=c("kl", "kle", "lek", "ekl"), 
      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
    ) %>%
    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
    na.omit()

>>>>

<<sigma_graph, fig.pos="H", fig.align='center', fig.width=7.5, fig.height=3.3, fig.cap="Elasticities of substitution~($\\sigma$) for the UK.", eval=FALSE, include=FALSE>>=
sigma_graph <- function(data){
  sigma_graph_data <- 
    data %>% 
    select(Country, CSP, flavor, energy, nest, 
           sigma_12, sigma_23, sigma_13, 
           sigma_12_3, sigma_23_1, sigma_13_2) %>%
    mutate(nest = plyr::mapvalues( # Change nest to a nicer-looking nest string
      nest, 
      from=c("kl", "kle", "lek", "ekl"), 
      to=c("kl", "(kl)e", "(le)k", "(ek)l"))
    ) %>%
    gather(variable, value, sigma_12, sigma_23, sigma_13, sigma_12_3, sigma_23_1, sigma_13_2) %>%
    mutate(label = paste(CSP, flavor, energy, nest, variable, sep=", ")) %>%
    na.omit()

@@

<<sigma_graph_3, fig.pos="H", fig.align='center', fig.width=8.5, fig.height=5, out.width="0.9\\textwidth", fig.cap="Elasticities of substitution~($\\sigma$) with factors of production on the vertical facet.">>=
breaks_labels = c(0.01, 1, 100)
p <- 
ggplot(
  AllCoeffs %>% 
    gather(type, value, matches("sigma")) %>% 
    filter(!is.na(value)) %>% 
    filter(! type %in% c("sigma", "sigma_1")) %>%
    mutate(Model = interaction(nest, CSP, sep = " ", drop=TRUE),
           Inputs = flavor
           )
  ) + 
  geom_point(aes(x=value, y=type, 
                 shape = Model, fill=Model, size=Model,
                 color=Inputs
                 )
                 #position = position_jitter(height=0.2, width=0)
             ) + 
  # facet_grid( type ~ Country, scales = "free_y" ) + 
  facet_grid( Inputs ~ Country) + 
  scale_x_log10(limits = c(0.001,2000), breaks=breaks_labels, labels=breaks_labels) +
  xlab("") +
  geom_vline(xintercept = 1, color="gray50", size=0.2) +
  ylab("") +
  xy_theme() #+
#   theme(
#     legend.position="top",
#     strip.text.y = element_blank())
